My First knitr Document
========================

#First level heading
Raymond

## Introduction

This is some text here

```{r}
set.seed(1)
x = rnorm(100)
mean(x)
```

```{r computetime, echo=FALSE}
time = format(Sys.time(), "%a %b %d %X %Y")
rand = rnorm(1)
```
The current time is `r time`. My favorite random number is `r rand`.


#Next
Simulating some data
```{r simulatedata, echo=TRUE}
x = rnorm(100); y = x + rnorm(100, sd=0.5)
```

Scatterplot of the data
```{r scatterplot, fig.height=4}
par(mar = c(5, 4, 1, 1), las = 1)
plot(x, y, main = "My Simulated Data")
```

#Next
Making tables with xtable

```{r fitmodel}
library(datasets)
data(airquality)
fit = lm(Ozone ~ Wind + Temp + Solar.R, data = airquality)
```
Here is a table of regression coefficients

```{r showtable, results = "asis"}
library(xtable)
xt = xtable(summary(fit))
print(xt, type = "html")
```




```{r loadData, echo=TRUE}
aa = read.csv("D:\\Users\\msboon\\Desktop\\For Data science coursera\\Reproducible Research\\repdata%2Fdata%2Factivity\\activity.csv")
colnames(aa)
```

```{r totalStepsPerDay, echo=TRUE}
library(lubridate)
table1 = matrix(data=NA, ncol  =4, nrow = length(unique(aa$date)))
colnames(table1) = c("Day", "Total steps", "Mean steps", "Median steps")
all_dates = as.character(unique(aa$date))
for(i in 1:length(all_dates)){
     mdate = aa[which(aa$date==all_dates[i]),]
     table1[i, ] = c(all_dates[i], sum(mdate$steps),round(mean(mdate$steps),3), median(mdate$steps))
}
#View(table1)

```
Now to create a histogram of the sum of daily steps, the non-NA ones

```{r histogram, echo=TRUE}
library(ggplot2)
histTable = data.frame(Date = 1:length(unique(aa$date)), Total_Steps = as.numeric(table1[,2]), stringsAsFactors=FALSE)

qplot(na.omit(histTable$Total_Steps), geom="histogram", bins=30,xlab="Total number of steps")
```


Now reporting daily mean and median
```{r tableMeanMedian, echo=TRUE, results ="asis"}
table1 = na.omit(table1)
meanMedian = data.frame(row.names =table1[,1], Mean_Steps = table1[,3], Median_Steps = table1[,4], stringsAsFactors=FALSE)
xmm = xtable(meanMedian)
print(xmm, type="html")


```


#Now the average daily activity pattern

```{r dailyPattern, echo=TRUE}


```



